Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-09 doc/PRF2022/PRF_main.tex
PRF_main.tex updates

Figure~\ref{fig:relax}a shows the initial configurations with orientations of 198-particle and 60- particle cases. 
Case (i) with $b = 1$, mimicks an amphiphilic particle.
The boundary condition $g$ is everywhere nonnegative,
takes the value $0$ on the
hydrophilic head,
and takes the maximum value $a$ on the
hydrophobic tail. 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)). The inset shows the equilibrium 
state for 60-particle run that forms multiple bilayers with a vesicle like structure.

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  A:  The free energy \eqref{eq:free_energy} decreases
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations as shown in Figure \ref{fig:relax}b--d, respectively.
    The solid curves are the energies for the $N_b=60$ cases and  
    the dashed curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. We use different colors to distinguish from boundary conditions.
    B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. 
    The curve styles are identical to the ones in panel A.
    The near-equilibrium configurations depend on the initial configuration and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trend in self-assembly in term of the local order parameter. The results of the striated configuration depend on the initial setup.
  }
\end{figure}

Figure~\ref{fig:relax_energy}a tracks the free energy profiles for all relaxation runs. For 198-particle cases, we normalized the energies by 60/198 and the results show that all energies decrease with good agreements in all boundary conditions. This can be considered as an evidence that the proposed model with specified boudary condtions is independent of number of particles.
Figure~\ref{fig:relax_energy}b 
measures the orientational order parameter $\tilde{S}_2$. Both bilayer and multilamellar 
structures have similar trends in small and large systems. The aggregation for striated configurations may have one or more different pattern formations when the number of particles is varied.

@@

The bilayer is subject to a shear background flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the shear rate. 
Figure~\ref{fig:BC1_shear} (a)--(c)
shows snapshots of the vesicle when $\dot\gamma= 0.05,0.075,0.01$.
The free energies (Figure~\ref{fig:BC1_shear}d) are relatively constant and 
lower shear rate results a smaller orientational parameter (Figure~\ref{fig:BC1_shear}e). The supplementary movies show that these bilayers merge and form a work-like shape in higher 
shear flows. Figure~\ref{fig:BC1_shear}f shows that the strain parameter diverges when 
the shear rate is large enough.

@@

In Figure~\ref{fig:Ves_shear} (a)--(c), the vesicle in a shear flow undergoes the familiar tank-treading deformation. 
Our previous paper \cite{Fu2022_JFM} studied the geometry,
intermonolayer slip, and critical shear rates $\gamma^*=0.066$
for vesicles comprised of amphiphilic Janus particles. 
Here $\dot\gamma=0.05, 0.066, 0.075$ and there are jumps in energies (Figure \ref{fig:Ves_shear}d, long and short dashed curves) due to the breaking of the vesicle into two
components. There is greater variation in the order parameter $\tilde{S}_2(t)$ as well
with a baseline value around $0.7$
(Figure \ref{fig:Ves_shear}e, dashed curve).
The oscillations occur due to the orbit of the two bilayer components, and $\tilde{S}_2(t)$ increases to about $0.9$ when the components are nearly parallel and slide past one another.
For the lowest shear rate case, it has nearly perfect orientational parameter due to the steady tank-treading motion.
Positional order, however, diverges since the two component configuration
is uncorrelated to the initial circular configuration (Figure \ref{fig:Ves_shear}f, dashed curve).

@@

Figure~\ref{fig:BC1_TG}a--c are the snapshots when $V_0=0.1,0.15,0.2$, respectively.
This initial configuration in TG flow encounters a number of fusion but there is no clear trend for
all measures with respect to the flow strengths.

@@

For a vesicle in a Taylor-Green flow, Figure~\ref{fig:ves_TG}a--c are configurations at $t=0.2 \mu$s where $V_0=0.1,0.15,0.2$. Figure~\ref{fig:ves_TG}d--f indicates that the rupture occurs when the energy and strain parameter are significant larger and the orientational parameter is much lower than other cases.

@@

We vary the cell size by tuning the parameter $l$ in \eqref{eq:tg_flow}.  Figure~\ref{fig:BTG_Scale}a--d show the deformation of a vesicle in a Taylor-Green flow when $V_0=0.1$ and arrows indicate rotating directions. Figure~\ref{fig:BTG_Scale}e presents that the area $A/A_0$ decreases during the simulations and the inset shows constant total lengths $L/L_0$ for all cases where $A_0$ and $L_0$ are initial enclose area and midplane length.
%A/A0 plot with no monotonic trend.
One interesting finding is that the number of cells affects the directions of structure rotation.

@@

We place a 60-particle multilamellar configuration (inset of Figure~\ref{fig:BC2_shear}a) in shear flows where $\dot\gamma=0.05, 0.1, 0.15$. Quantities such as energies, orientational parameter, and positional parameter (Figure~\ref{fig:BC2_shear}d--f) follow the same trend where they increases as shear rate increases. 
Comparing with bilayer structures, Figure~\ref{fig:BC2_shear}a--c demonstrate that the multilamellar ones are more rigid in shear flow and the rupture phenomenon can be observed 
when the shear rate is high enough.

@@

For multilamellar structure in a Taylor-Green flow, as shown in Figure~\ref{fig:BC2_TG}a--b, lower flow strengths such as $V_0=0.1,0.15$ do not reach a critical flow rate for structural disorder. 
When $V_0=0.2$ (Figure~\ref{fig:BC2_TG}c), the flow is strong enough to separate the structure
into multiple groups within the cells. In all deformation measures, a similar trend in shear flow case is observed, see Figure~\ref{fig:BC2_TG}d--f.

@@

We place the striated configuration in a shear flow when $\dot\gamma=0.1, 0.125, 0.15$ and 
the snapshots at $t=0.1 \mu$s are shown in Figure~\ref{fig:BC3_shear}a--c.
Break-up deformation measures (igure~\ref{fig:BC3_shear}d--f) are similar to vesicle in shear flow case. Notably, for low shear rates, oscillatory behaviours are investigated in energies, orientational and positional parameters.

@@

For a striated configuration in a Taylor-Green flow, numerical experiments have shown that one needs to choose relative higher flow strengths than other boundary conditions to reach structural disorder. Figure~\ref{fig:BC3_TG}a--c are configurations for $V_0=0.2, 0.25, 0.3$ at $t=0.4 \mu$s.
Figure~\ref{fig:BC3_TG}d--f show that the threshold for having clear rupture is between $V_0=0.2$ and $V_0=0.25$ and a huge jump in measures occurs soon after the flow is turned on.

@@

>>>>

Figure~\ref{fig:relax}(a) shows the initial configurations with orientations of 198-particle and 60- particle cases. 
Case (i) with $b = 1$, mimicks an amphiphilic particle.
The boundary condition $g$ is everywhere nonnegative,
takes the value $0$ on the
hydrophilic head,
and takes the maximum value $a$ on the
hydrophobic tail. 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)). The inset shows the equilibrium 
state for 60-particle run that forms multiple bilayers with a vesicle like structure.

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  Panel (a) shows that the free energy \eqref{eq:free_energy} decreases
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}(a)
    and the final energies are for the near-equilibrium
    configurations as shown in Figure \ref{fig:relax}(b)--(d), respectively.
    The solid curves are the energies for the $N_b=60$ cases and  
    the dashed curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. We use different colors to distinguish from boundary conditions.
    Panel (b) shows the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs. 
    The curve styles are identical to the ones in panel (a).
    The near-equilibrium configurations depend on the initial configurations and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trends in orientational parameters. The results of the striated configuration depend on the initial geometrical setup.
  }
\end{figure}

Figure~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs. For 198-particle cases, we normalized the energies by 60/198 and the results show that all energies decrease with good agreements in all boundary conditions. This can be considered as an evidence that the proposed model with specified boudary condtions is independent of number of particles.
Figure~\ref{fig:relax_energy}(b) 
measures the orientational order parameter $\tilde{S}_2$. Both bilayer and multilamellar 
structures have similar trends in small and large systems. The aggregation for striated configurations may have one or more different pattern formations when the number of particles is varied.

@@

The bilayer is subject to a shear background flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the shear rate. 
Figure~\ref{fig:BC1_shear}(a)--(c)
shows snapshots of the vesicle when $\dot\gamma= 0.05,0.075,0.01$.
The free energies (Figure~\ref{fig:BC1_shear}(d)) are relatively constant and 
lower shear rate results a smaller orientational parameter (Figure~\ref{fig:BC1_shear}(e)). The supplementary movies show that these bilayers merge and form a work-like shape in higher 
shear flows. Figure~\ref{fig:BC1_shear}(f) shows that the strain parameter diverges when 
the shear rate is large enough.

@@

In Figure~\ref{fig:Ves_shear} (a)--(c), the vesicle in a shear flow undergoes the familiar tank-treading deformation. 
Our previous paper \cite{Fu2022_JFM} studied the geometry,
intermonolayer slip, and critical shear rates $\gamma^*=0.066$
for vesicles comprised of amphiphilic Janus particles. 
Here $\dot\gamma=0.05, 0.066, 0.075$ and there are jumps in energies (Figure \ref{fig:Ves_shear}(d), long and short dashed curves) due to the breaking of the vesicle into two
components. There is greater variation in the order parameter $\tilde{S}_2(t)$ as well
with a baseline value around $0.7$
(Figure \ref{fig:Ves_shear}(e), dashed curve).
The oscillations occur due to the orbit of the two bilayer components, and $\tilde{S}_2(t)$ increases to about $0.9$ when the components are nearly parallel and slide past one another.
For the lowest shear rate case, it has nearly perfect orientational parameter due to the steady tank-treading motion.
Positional order, however, diverges since the two component configuration
is uncorrelated to the initial circular configuration (Figure \ref{fig:Ves_shear}(f), dashed curve).

@@

Figure~\ref{fig:BC1_TG}(a)--(c) are the snapshots when $V_0=0.1,0.15,0.2$, respectively.
This initial configuration in TG flow encounters a number of fusion but there is no clear trend for
all measures with respect to the flow strengths.

@@

For a vesicle in a Taylor-Green flow, Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\  \mu$s where $V_0=0.1,0.15,0.2$. Figure~\ref{fig:ves_TG}(d)--(f) indicates that the rupture occurs when the energy and strain parameter are significant larger and the orientational parameter is much lower than other cases.

@@

We vary the cell size by tuning the parameter $l$ in \eqref{eq:tg_flow}.  Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a Taylor-Green flow when $V_0=0.1$ and $t = 1\ \mu$s where arrows indicate rotating directions. Figure~\ref{fig:BTG_Scale}(e) presents that the area $A/A_0$ decreases during the simulations and the inset shows constant total lengths 
$L/L_0$ for all cases where $A_0$ and $L_0$ are initial enclose area and midplane length.
%A/A0 plot with no monotonic trend.
One interesting finding is that the number of cells affects the directions of structure rotation.

@@

We place a 60-particle multilamellar configuration (inset of Figure~\ref{fig:BC2_shear}(a)) in shear flows where $\dot\gamma=0.05, 0.1, 0.15$. Quantities such as energies, orientational parameter, and positional parameter (Figure~\ref{fig:BC2_shear}(d)--(f)) follow the same trend where they increases as shear rate increases. 
Comparing with bilayer structures, Figure~\ref{fig:BC2_shear}(a)--(c) demonstrate that the multilamellar ones are more rigid in shear flow and the rupture phenomenon can be observed 
when the shear rate is high enough.

@@

For multilamellar structure in a Taylor-Green flow, as shown in Figure~\ref{fig:BC2_TG}(a)--(b), lower flow strengths such as $V_0=0.1,0.15$ do not reach a critical flow rate for structural disorder. 
When $V_0=0.2$ (Figure~\ref{fig:BC2_TG}(c)), the flow is strong enough to separate the structure
into multiple groups within the cells. In all deformation measures, a similar trend in shear flow case is observed, see Figure~\ref{fig:BC2_TG}(d)--(f).

@@

We place the striated configuration in a shear flow when $\dot\gamma=0.1, 0.125, 0.15$ and 
the snapshots at $t=0.1\ \mu$s are shown in Figure~\ref{fig:BC3_shear}(a)--(c).
Break-up deformation measures (igure~\ref{fig:BC3_shear}(d)--(f)) are similar to vesicle in shear flow case. Notably, for low shear rates, oscillatory behaviours are investigated in energies, orientational and positional parameters.

@@

For a striated configuration in a Taylor-Green flow, numerical experiments have shown that one needs to choose relative higher flow strengths than other boundary conditions to reach structural disorder. Figure~\ref{fig:BC3_TG}(a)--(c) are configurations for $V_0=0.2, 0.25, 0.3$ at $t=0.4\  \mu$s.
Figure~\ref{fig:BC3_TG}(d)--(f) show that the threshold for having clear rupture is between $V_0=0.2$ and $V_0=0.25$ and a huge jump in measures occurs soon after the flow is turned on.

@@

We notice that the strain parameter are relatively higher (of order 10) in shear flows or not confining flows comparing with ones of order 1 in cases using Taylor-Green flows when rupture occurs. In order to make the structure disorder, the striated structures need the highest flow strength or shear rate in all three boundary conditions. Moreover, this can be interpreted by having higest free energy calculated from striated structures.
